Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-10-28 Report/convergence_centralized.tex
updated stationarity

%\review{We use the following notations to discuss the convergence proof. Since Algorithm \ref{algo-1} involves two nested iterations, \textit{i.e.}, one for \ac{SCA} and another one for \ac{AO}, we denote \ac{AO} step by a superscript \me{(i)} and \ac{SCA} iteration by a subscript \me{k}. Let \me{\mx}, \me{\my}, and \me{\mz} be the stacked vector all transmit precoders, receive beamformers, and other optimization variables present in the formulations \eqref{eqn-6} and \eqref{eqn-mse-1} respectively. Since Algorithm \ref{algo-1} includes two \ac{SCA} iterations performed until convergence in each \ac{AO} iteration, let us now consider \ac{AO} step \eqn{i} for fixed \eqn{\my}. The solution obtained at the \eqn{\ith{k}} \ac{SCA} step is represented as \eqn{\mx=\iter{\mx}{k}{i}} and \eqn{\mz=\iter{\mz}{k}{i}}. As \eqn{k \rightarrow \infty}, the objective sequence converges, and the corresponding solution obtained is denoted as \me{\iter{\mx}{\lpointx}{i}} and \me{\iter{\mz}{\lpointx|\my}{i}}. Similarly, for fixed \eqn{\mx} and as \eqn{k \rightarrow \infty}, the corresponding solution obtained is represented as \me{\my = \iter{\my}{\lpointx}{i}} and \me{\mz = \iter{\mz}{\lpointx|\mx}{i}} respectively.}

@@

%The minimum of the norm in the objective is \me{\|x\|_q > -\infty}, therefore, it is bounded below. The objective function is Lipschitz continuous over the feasible set. The objective function is bounded from above as well, since the feasible set is bounded. %The objective function in \eqref{eqn-6} and \eqref{eqn-mse-1} is continuous and approaches \me{\infty} as \me{\mbf{t}_k \rightarrow \infty}, and therefore it is coercive in the feasible set. %Using conditions (a) and (b), we can guarantee the existence of a minimizer to the problem in \eqref{eqn-6} and \eqref{eqn-mse-1}.

@@

%since \eqn{\iter{\mbf{z}}{k+1}{i}} is the solution. Using \eqref{strict_monotonicity} and \eqn{\iter{\mbf{z}}{k}{i} \in \iter{\mc{X}}{k}{i}}, we can show that \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})} holds in each \ac{SCA} step unless \eqn{\mbf{z}_{k}^{(i)} \rightarrow \mbf{z}_{\lpoint}^{(i)}} as \eqn{k \rightarrow \infty}. Now using the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic, and (ii) the uniqueness of the minimizer (see \eqref{strict_monotonicity}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured \cite{scutari2010convex}. Now, by using the fact that the objective sequence is strictly nonincreasing and bounded, we can ensure the convergence of objective sequence in each \ac{AO} step \eqn{{i}} and \reviewF{\eqn{\mbf{z}_{\lpoint}^{(i)} \triangleq \{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\}} is the solution obtained upon convergence of the objective sequence \eqn{\{f(\mbf{z}_k^{(i)})\}} in the \eqn{\ith{i}} \ac{AO} iteration.}

@@

%Note that \eqref{s_ineq} holds with strict inequality in each update as \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})}, unless \eqn{\mbf{z}_{k}^{(i)} = \mbf{z}_{k+1}^{(i)}}, which occurs at \eqn{\mbf{z}_{k}^{(i)} \rightarrow \mbf{z}_{\lpoint}^{(i)}} as \eqn{k \rightarrow \infty}. Using the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic \cite{marks1978technical}, and (ii) the uniqueness of the minimizer (see \eqref{s_ineq_g}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured. However, if \eqn{\hat{f}} is used as the objective in \eqref{con-m}, then strict monotonicity of \eqn{\{\hat{f}(\mbf{z}^{(i)}_k)\}} cannot be guaranteed due to the existence of multiple solutions.

@@

%	since \eqn{\iter{\mbf{z}}{k+1}{i}} is the minimizer of \eqref{con-m}. Note that \eqref{strict_monotonicity} holds with strict inequality in each update as \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})}, unless \eqn{\mbf{z}_{k}^{(i)} = \mbf{z}_{k+1}^{(i)}}, which occurs at \eqn{\mbf{z}_{k}^{(i)} \rightarrow \mbf{z}_{\lpoint}^{(i)}} as \eqn{k \rightarrow \infty}. Using the facts that (i) the sequence \eqn{\{f(\mbf{z}^{(i)}_k)\}} generated by the \ac{SCA} approach is monotonic \cite{marks1978technical}, and  (ii) the uniqueness of the minimizer in each \ac{SCA} step (see \eqref{strict_monotonicity}), we can ensure the strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}}. However, if \eqn{\hat{f}} is used as the objective in \eqref{con-m}, then strict monotonicity of \eqn{\{\hat{f}(\mbf{z}^{(i)}_k)\}} cannot be guaranteed due to the existence of multiple solutions.

@@

%	where the equality is valid when \eqn{\mbf{z}_{k}^{(i)} = \mbf{z}_{k+1}^{(i)}}, \textit{i.e.}, as \eqn{k\rightarrow\infty}, \eqn{\mbf{z}_{k}^{(i)} \rightarrow \mbf{z}_{\lpoint}^{(i)}}. Using the facts that (i) the sequence \eqn{\{f(\mbf{z}^{(i)}_k)\}} generated by the \ac{SCA} approach is monotonic \cite{marks1978technical}, and  (ii) the uniqueness of the minimizer in each \ac{SCA} step (see \eqref{strict_monotonicity}), we can ensure the strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}}. However, if \eqn{\hat{f}} is used in the objective of \eqref{con-m}, then the limit point is not unique, \textit{i.e.}, \eqn{\{\exists \mbf{z} \in \mc{X}_{\lpoint}^{(i)} \vert \hat{f}(\mbf{z}) = \hat{f}(\mbf{z}_{\lpoint}^{(i)})\}}, and therefore the sequence generated by \eqref{con-m} with \eqn{\hat{f}} is not strictly monotonic.

@@

%	Similarly, we can ensure strict monotonicity of the objective \eqref{mod_obj} while alternating the optimization variables from \eqn{\mx,\mz} to \eqn{\my,\mz} in the \eqn{\ith{i}} \ac{AO} iteration. Since the limit point \eqn{\{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\mx}{i}\}} is also included in the feasible set \eqn{\mc{Y}_{0}^{i}}, the objective function follows \eqref{fixed_point} in strict sense unless the overall sequence \eqn{\{\mbf{z}_{\lpoint}^{i} \}} converges to a limit point as \eqn{i \rightarrow \infty}.}

@@

%%Additionally, we can also ensure the convergence of \eqn{\{\hat{f}(\ma^t)\}}, since the regularization term in \eqref{mod_obj} vanishes as \eqn{t \rightarrow \infty}, \eqn{\|\ma - \ma^t\|^2 \rightarrow 0}.

@@

%Therefore, we can only claim that every limit point of the sequence \eqn{\{\ma^t\}} is a stationary point, \textit{i.e.,} the limit point of every convergent subsequence is a stationary point. To prove that, let us consider a subsequence \eqn{\{\ma^{t_j} \, | \, j = 0,1,\dotsc\}} of \eqn{\{\ma^t\}} that converges to a limit point \eqn{\bar{\ma}}, where \eqn{\bar{\ma} = \lim_{j \rightarrow \infty} \ma^{t_j}}. It follows from \eqref{con-convergence}, \eqref{strict_monotonicity}, and \eqref{fixed_point} that

@@

%Eq. \eqref{seq_mon} holds strictly while alternating the optimization variables as shown in \eqref{fixed_point}. Now, by taking the limit as \eqn{j \rightarrow \infty} and by using the continuity of objective function \eqn{f}, we obtain

@@

%\lim_{j \rightarrow \infty} f(\ma^{t_j}) = f(\lim_{j \rightarrow \infty} \ma^{t_{j}}) = f(\bar{\ma}).

@@

%Using strict monotonicity in \eqn{\{f(\ma^{t_j})\}} and the fact that as \eqn{j \rightarrow \infty}, \eqn{|f(\ma^{t_{j}}) - f(\ma^{t_{j+1}})| \rightarrow 0}, we can show that limit point \eqn{\bar{\ma}} satisfies the optimality condition \cite[Prop. 2.1.2]{bertsekas1999nonlinear} as 

@@

%where \eqn{\mc{Q}} is a convex subset defined by \eqref{con-dc-m} and \eqref{con-cvx-blk-m} as \eqn{k \rightarrow \infty, i \rightarrow \infty}. Hence, the limit point \eqn{\bar{\ma}} is a stationary point of \eqref{con-m} as \eqn{k \rightarrow \infty, i \rightarrow \infty}.

@@

%The relation between \eqref{kkt_expr} and \eqref{kkt_mod_expr} is evident by the following facts: (i) The quadratic term \eqn{\|\ma - \ma^{t_j}\|^2} in \eqref{mod_obj} vanishes as \eqn{j \rightarrow \infty, \ma^{t_j} \rightarrow \bar{\ma}}, since we assume that \eqn{\bar{\ma}} is the limit point of convergent subsequence \eqn{\{\ma^{t_j}\}}. Therefore, the gradient evaluated at \eqn{\bar{\ma}} satisfies \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})}. (ii) Additionally, by using the relation in \eqref{con-relax}, the gradient of the constraint \eqref{con-dc} evaluated at \eqn{\bar{\ma}} is given as

@@

%\review{Note that the strict monotonicity of the objective is guaranteed using the strong convexity of \eqn{f} in Section \ref{mcity}. Therefore, all the above requirements are satisfied by algorithm \eqref{g-algo}}. Using \cite{zangwill1969nonlinear} and \cite[Th. 3.1]{meyer1976sufficient}, we can show that (i) all limit points will be a fixed point, (ii) \eqn{f(\iterate{\ma}{i}) \rightarrow f(\ma^\lpoint)}, where \eqn{\ma^\lpoint} is a fixed point, and (iii) \eqn{\ma^\lpoint} is a regular point, \textit{i.e.}, \eqn{\|\iterate{\ma}{i} - \mc{A}(\iterate{\ma}{i}) \| \rightarrow 0}. Even though the fixed points in the set \me{\mc{F}^\lpoint} can be achieved by the algorithm \me{\mc{A}} for different initial points, the algorithm \me{\mc{A}} achieves a unique limit point, \textit{i.e.}, \me{\mc{F}^\lpoint = \{\ma^\lpoint\}}, once a feasible point is chosen to be the operating point while initializing \me{\mc{A}}.

@@

%\item[(ii)] \eqn{f(\iterate{\ma}{i}) \rightarrow f(\ma^\lpoint)}, where \eqn{\ma^\lpoint} is a fixed point,
%\item[(iii)] \eqn{\ma^\lpoint} is a regular point, \textit{i.e.} \eqn{\|\iterate{\ma}{i} - \iterate{\ma}{i+1} \| \rightarrow 0}.

@@

%\review{Upon satisfying the conditions (a)-(d), we have shown that the sequence \eqn{\{\iterate{\ma}{i}\}} generated by \eqn{\mc{A}} converges to a limit point \eqn{\ma^{\lpoint}} as \eqn{i \rightarrow \infty}. Now, to show that \eqn{\ma^{\lpoint}} is a stationary point of \eqref{con}, it must satisfy the \ac{KKT} gradient condition of \eqref{con}, \textit{i.e.},

@@

%The relation between \eqref{kkt_mod_expr} and \eqref{kkt_expr} is evident by the following facts: (i) The quadratic term \eqn{\|\ma - \ma^{(i)}\|^2} in \eqref{mod_obj} vanishes as \eqn{i \rightarrow \infty, \ma^{(i)} \rightarrow \ma^{\lpoint}}, since \eqn{\ma^{\lpoint}} is the fixed point of \eqn{\mc{A}}. Therefore, the gradient evaluated at \eqn{\ma^{\lpoint}} satisfy \eqn{\nabla {f}(\ma^{\lpoint}) = \nabla \hat{f}(\ma^{\lpoint})}. (ii) Additionally, by using the relation in \eqref{con-relax}, the gradient of the constraint \eqref{con-dc} evaluated at \eqn{\ma^{\lpoint}} is given as

@@

%In this section, we show that the limit point \eqn{\ma^{\lpoint}} of the sequence \eqn{\{\iterate{\ma}{i}\}}, obtained from \eqn{\mc{A}} as \eqn{i \rightarrow \infty} is a stationary point of the original nonconvex problem in \eqref{con}. In order for \eqn{\ma^{\lpoint}} to be a stationary point, it must satisfy the \ac{KKT} conditions of \eqref{con} and the Slater's constraint qualifications. Note that all points satisfies \eqn{\iterate{\ma}{i} \in \mc{Y}_\lpoint^{(i)} \subset \mc{F}}, and therefore the limit point \eqn{\ma^{\lpoint}} satisfies the constraint qualifications of the problem \eqref{con}.

@@

%\review{Let \eqn{\ma^{\lpoint}} be the limit point of the sequence of iterates \eqn{\{\iterate{\ma}{i}\}} generated by the algorithm \eqn{\mc{A}} as \eqn{i \rightarrow \infty}. The limit point \eqn{\ma^\lpoint} is a stationary point of \eqref{con} if it satisfies the \ac{KKT} conditions. 

@@

%%where \eqn{\mc{Y}^{\lpoint}} is the feasible set of \eqref{con-m} upon convergence, \textit{i.e.}, \eqn{\mc{Y}_{\lpoint}^{i}} as \eqn{i \rightarrow \infty}. 

@@

%Using (a),(b),(c) and (d), we can show that \eqn{\|\ma^{(i)} - \mc{A}(\ma^{(i)})\| \rightarrow 0} as \eqn{i \rightarrow \infty}, which is the limit point of the algorithm \eqn{\mc{A}}.

@@

%%In order for \eqn{\ma^{\lpoint}} to be stationary point, it must satisfy the \ac{KKT} conditions of \eqref{con}. In each iteration, the algorithm \eqn{\mc{A}} in \eqref{g-algo} finds a point \eqn{\iterate{\ma}{i} \in \mc{F}} with \eqn{f(\iterate{\ma}{i}) < f(\iterate{\ma}{i-1})}, therefore, it satisfies all the constraints of \eqref{con}. Since the feasible set is compact and strict monotonicity is ensured, as \eqn{i \rightarrow \infty}, the objective no longer decreases as the algorithm \eqn{\mc{A}(\ma^{\lpoint}) = \ma^{\lpoint}} finds a unique \eqn{\ma^{\lpoint} \in \mc{F}^{\lpoint}} due to the strong convexity of \eqn{f}.

@@

%%for some Lagrange multipliers \eqn{\mu_i \geq 0}. Using \eqref{con-relax} in \eqref{kkt_expr}, we can ensure the equivalence of the gradient between \eqref{con} and \eqref{con-m}. Moreover, \eqn{\ma^{\lpoint}} is a regular point \textit{i.e.} \eqn{\|\iterate{\ma}{i} - \iterate{\ma}{i+1} \| \rightarrow 0} as \eqn{i \rightarrow 0}. Now, with the above conditions and by using \cite[Th. 2 and 11]{scutari_1} and \cite[Prop. 3.2]{amir}, we can show that the fixed points obtained by \me{\mc{A}} under the mapping \me{f} is a stationary point of the nonconvex problem \eqref{con}.

@@

%To show the limit point of the sequence of iterates \me{\{\iterate{\ma}{i}\}} is a stationary point, it must satisfy the \ac{KKT} conditions of the problem in \eqref{con}. As \me{i \rightarrow \infty}, the objective converges as

@@

The following conditions are required to show the convergence of Algorithm \ref{algo-1}, which is used to solve problems \eqref{eqn-6} and \eqref{eqn-mse-1} in an iterative manner.
\begin{itemize}
\item[(a)] Objective function should be bounded below
\item[(b)] Feasible set should be compact
\item[(c)] Sequence of objective values should be strictly decreasing
\item[(d)] Uniqueness of the minimizer in each step.
\end{itemize}
\review{The conditions (a), (b), and (c) are required to prove the convergence of objective sequence generated by Algorithm \ref{algo-1}. However, to ensure strict monotonicity of the objective sequence, we require the additional condition (d). Therefore, by assuming (a), (b), and (c) are satisfied by Algorithm \ref{algo-1}, the convergence of the objective sequence can be shown using \cite[Th. 3.14]{rudin1964principles}. Finally, by using the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1}, we show that \reviewF{every limit point of the sequence of iterates generated by Algorithm \ref{algo-1} is a stationary point of nonconvex problems \eqref{eqn-6} and \eqref{eqn-mse-1}}. The term iterates correspond to the stacked vector of solution variables obtained in each iteration.}

>>>>

%\review{We use the following notations to discuss the convergence proof. Since Algorithm \ref{algo-1} involves two nested iterations, \textit{i.e.}, one for \ac{SCA} and another one for \ac{AO}, we denote \ac{AO} step by a superscript \me{(i)} and \ac{SCA} iteration by a subscript \me{k}. Let \me{\mx}, \me{\my}, and \me{\mz} be the stacked vector all transmit precoders, receive beamformers, and other optimization variables present in the formulations \eqref{eqn-6} and \eqref{eqn-mse-1} respectively. Since Algorithm \ref{algo-1} includes two \ac{SCA} iterations performed until convergence in each \ac{AO} iteration, let us now consider \ac{AO} step \eqn{i} for fixed \eqn{\my}. The solution obtained at the \eqn{\ith{k}} \ac{SCA} step is represented as \eqn{\mx=\iter{\mx}{k}{i}} and \eqn{\mz=\iter{\mz}{k}{i}}. As \eqn{k \to \infty}, the objective sequence converges, and the corresponding solution obtained is denoted as \me{\iter{\mx}{\lpointx}{i}} and \me{\iter{\mz}{\lpointx|\my}{i}}. Similarly, for fixed \eqn{\mx} and as \eqn{k \to \infty}, the corresponding solution obtained is represented as \me{\my = \iter{\my}{\lpointx}{i}} and \me{\mz = \iter{\mz}{\lpointx|\mx}{i}} respectively.}

@@

%The minimum of the norm in the objective is \me{\|x\|_q > -\infty}, therefore, it is bounded below. The objective function is Lipschitz continuous over the feasible set. The objective function is bounded from above as well, since the feasible set is bounded. %The objective function in \eqref{eqn-6} and \eqref{eqn-mse-1} is continuous and approaches \me{\infty} as \me{\mbf{t}_k \to \infty}, and therefore it is coercive in the feasible set. %Using conditions (a) and (b), we can guarantee the existence of a minimizer to the problem in \eqref{eqn-6} and \eqref{eqn-mse-1}.

@@

%since \eqn{\iter{\mbf{z}}{k+1}{i}} is the solution. Using \eqref{strict_monotonicity} and \eqn{\iter{\mbf{z}}{k}{i} \in \iter{\mc{X}}{k}{i}}, we can show that \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})} holds in each \ac{SCA} step unless \eqn{\mbf{z}_{k}^{(i)} \to \mbf{z}_{\lpoint}^{(i)}} as \eqn{k \to \infty}. Now using the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic, and (ii) the uniqueness of the minimizer (see \eqref{strict_monotonicity}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured \cite{scutari2010convex}. Now, by using the fact that the objective sequence is strictly nonincreasing and bounded, we can ensure the convergence of objective sequence in each \ac{AO} step \eqn{{i}} and \reviewF{\eqn{\mbf{z}_{\lpoint}^{(i)} \triangleq \{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\}} is the solution obtained upon convergence of the objective sequence \eqn{\{f(\mbf{z}_k^{(i)})\}} in the \eqn{\ith{i}} \ac{AO} iteration.}

@@

%Note that \eqref{s_ineq} holds with strict inequality in each update as \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})}, unless \eqn{\mbf{z}_{k}^{(i)} = \mbf{z}_{k+1}^{(i)}}, which occurs at \eqn{\mbf{z}_{k}^{(i)} \to \mbf{z}_{\lpoint}^{(i)}} as \eqn{k \to \infty}. Using the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic \cite{marks1978technical}, and (ii) the uniqueness of the minimizer (see \eqref{s_ineq_g}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured. However, if \eqn{\hat{f}} is used as the objective in \eqref{con-m}, then strict monotonicity of \eqn{\{\hat{f}(\mbf{z}^{(i)}_k)\}} cannot be guaranteed due to the existence of multiple solutions.

@@

%	since \eqn{\iter{\mbf{z}}{k+1}{i}} is the minimizer of \eqref{con-m}. Note that \eqref{strict_monotonicity} holds with strict inequality in each update as \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})}, unless \eqn{\mbf{z}_{k}^{(i)} = \mbf{z}_{k+1}^{(i)}}, which occurs at \eqn{\mbf{z}_{k}^{(i)} \to \mbf{z}_{\lpoint}^{(i)}} as \eqn{k \to \infty}. Using the facts that (i) the sequence \eqn{\{f(\mbf{z}^{(i)}_k)\}} generated by the \ac{SCA} approach is monotonic \cite{marks1978technical}, and  (ii) the uniqueness of the minimizer in each \ac{SCA} step (see \eqref{strict_monotonicity}), we can ensure the strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}}. However, if \eqn{\hat{f}} is used as the objective in \eqref{con-m}, then strict monotonicity of \eqn{\{\hat{f}(\mbf{z}^{(i)}_k)\}} cannot be guaranteed due to the existence of multiple solutions.

@@

%	where the equality is valid when \eqn{\mbf{z}_{k}^{(i)} = \mbf{z}_{k+1}^{(i)}}, \textit{i.e.}, as \eqn{k\to\infty}, \eqn{\mbf{z}_{k}^{(i)} \to \mbf{z}_{\lpoint}^{(i)}}. Using the facts that (i) the sequence \eqn{\{f(\mbf{z}^{(i)}_k)\}} generated by the \ac{SCA} approach is monotonic \cite{marks1978technical}, and  (ii) the uniqueness of the minimizer in each \ac{SCA} step (see \eqref{strict_monotonicity}), we can ensure the strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}}. However, if \eqn{\hat{f}} is used in the objective of \eqref{con-m}, then the limit point is not unique, \textit{i.e.}, \eqn{\{\exists \mbf{z} \in \mc{X}_{\lpoint}^{(i)} \vert \hat{f}(\mbf{z}) = \hat{f}(\mbf{z}_{\lpoint}^{(i)})\}}, and therefore the sequence generated by \eqref{con-m} with \eqn{\hat{f}} is not strictly monotonic.

@@

%	Similarly, we can ensure strict monotonicity of the objective \eqref{mod_obj} while alternating the optimization variables from \eqn{\mx,\mz} to \eqn{\my,\mz} in the \eqn{\ith{i}} \ac{AO} iteration. Since the limit point \eqn{\{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\mx}{i}\}} is also included in the feasible set \eqn{\mc{Y}_{0}^{i}}, the objective function follows \eqref{fixed_point} in strict sense unless the overall sequence \eqn{\{\mbf{z}_{\lpoint}^{i} \}} converges to a limit point as \eqn{i \to \infty}.}

@@

%%Additionally, we can also ensure the convergence of \eqn{\{\hat{f}(\ma^t)\}}, since the regularization term in \eqref{mod_obj} vanishes as \eqn{t \to \infty}, \eqn{\|\ma - \ma^t\|^2 \to 0}.

@@

%Therefore, we can only claim that every limit point of the sequence \eqn{\{\ma^t\}} is a stationary point, \textit{i.e.,} the limit point of every convergent subsequence is a stationary point. To prove that, let us consider a subsequence \eqn{\{\ma^{t_j} \, | \, j = 0,1,\dotsc\}} of \eqn{\{\ma^t\}} that converges to a limit point \eqn{\bar{\ma}}, where \eqn{\bar{\ma} = \lim_{j \to \infty} \ma^{t_j}}. It follows from \eqref{con-convergence}, \eqref{strict_monotonicity}, and \eqref{fixed_point} that

@@

%Eq. \eqref{seq_mon} holds strictly while alternating the optimization variables as shown in \eqref{fixed_point}. Now, by taking the limit as \eqn{j \to \infty} and by using the continuity of objective function \eqn{f}, we obtain

@@

%\lim_{j \to \infty} f(\ma^{t_j}) = f(\lim_{j \to \infty} \ma^{t_{j}}) = f(\bar{\ma}).

@@

%Using strict monotonicity in \eqn{\{f(\ma^{t_j})\}} and the fact that as \eqn{j \to \infty}, \eqn{|f(\ma^{t_{j}}) - f(\ma^{t_{j+1}})| \to 0}, we can show that limit point \eqn{\bar{\ma}} satisfies the optimality condition \cite[Prop. 2.1.2]{bertsekas1999nonlinear} as 

@@

%where \eqn{\mc{Q}} is a convex subset defined by \eqref{con-dc-m} and \eqref{con-cvx-blk-m} as \eqn{k \to \infty, i \to \infty}. Hence, the limit point \eqn{\bar{\ma}} is a stationary point of \eqref{con-m} as \eqn{k \to \infty, i \to \infty}.

@@

%The relation between \eqref{kkt_expr} and \eqref{kkt_mod_expr} is evident by the following facts: (i) The quadratic term \eqn{\|\ma - \ma^{t_j}\|^2} in \eqref{mod_obj} vanishes as \eqn{j \to \infty, \ma^{t_j} \to \bar{\ma}}, since we assume that \eqn{\bar{\ma}} is the limit point of convergent subsequence \eqn{\{\ma^{t_j}\}}. Therefore, the gradient evaluated at \eqn{\bar{\ma}} satisfies \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})}. (ii) Additionally, by using the relation in \eqref{con-relax}, the gradient of the constraint \eqref{con-dc} evaluated at \eqn{\bar{\ma}} is given as

@@

%\review{Note that the strict monotonicity of the objective is guaranteed using the strong convexity of \eqn{f} in Section \ref{mcity}. Therefore, all the above requirements are satisfied by algorithm \eqref{g-algo}}. Using \cite{zangwill1969nonlinear} and \cite[Th. 3.1]{meyer1976sufficient}, we can show that (i) all limit points will be a fixed point, (ii) \eqn{f(\iterate{\ma}{i}) \to f(\ma^\lpoint)}, where \eqn{\ma^\lpoint} is a fixed point, and (iii) \eqn{\ma^\lpoint} is a regular point, \textit{i.e.}, \eqn{\|\iterate{\ma}{i} - \mc{A}(\iterate{\ma}{i}) \| \to 0}. Even though the fixed points in the set \me{\mc{F}^\lpoint} can be achieved by the algorithm \me{\mc{A}} for different initial points, the algorithm \me{\mc{A}} achieves a unique limit point, \textit{i.e.}, \me{\mc{F}^\lpoint = \{\ma^\lpoint\}}, once a feasible point is chosen to be the operating point while initializing \me{\mc{A}}.

@@

%\item[(ii)] \eqn{f(\iterate{\ma}{i}) \to f(\ma^\lpoint)}, where \eqn{\ma^\lpoint} is a fixed point,
%\item[(iii)] \eqn{\ma^\lpoint} is a regular point, \textit{i.e.} \eqn{\|\iterate{\ma}{i} - \iterate{\ma}{i+1} \| \to 0}.

@@

%\review{Upon satisfying the conditions (a)-(d), we have shown that the sequence \eqn{\{\iterate{\ma}{i}\}} generated by \eqn{\mc{A}} converges to a limit point \eqn{\ma^{\lpoint}} as \eqn{i \to \infty}. Now, to show that \eqn{\ma^{\lpoint}} is a stationary point of \eqref{con}, it must satisfy the \ac{KKT} gradient condition of \eqref{con}, \textit{i.e.},

@@

%The relation between \eqref{kkt_mod_expr} and \eqref{kkt_expr} is evident by the following facts: (i) The quadratic term \eqn{\|\ma - \ma^{(i)}\|^2} in \eqref{mod_obj} vanishes as \eqn{i \to \infty, \ma^{(i)} \to \ma^{\lpoint}}, since \eqn{\ma^{\lpoint}} is the fixed point of \eqn{\mc{A}}. Therefore, the gradient evaluated at \eqn{\ma^{\lpoint}} satisfy \eqn{\nabla {f}(\ma^{\lpoint}) = \nabla \hat{f}(\ma^{\lpoint})}. (ii) Additionally, by using the relation in \eqref{con-relax}, the gradient of the constraint \eqref{con-dc} evaluated at \eqn{\ma^{\lpoint}} is given as

@@

%In this section, we show that the limit point \eqn{\ma^{\lpoint}} of the sequence \eqn{\{\iterate{\ma}{i}\}}, obtained from \eqn{\mc{A}} as \eqn{i \to \infty} is a stationary point of the original nonconvex problem in \eqref{con}. In order for \eqn{\ma^{\lpoint}} to be a stationary point, it must satisfy the \ac{KKT} conditions of \eqref{con} and the Slater's constraint qualifications. Note that all points satisfies \eqn{\iterate{\ma}{i} \in \mc{Y}_\lpoint^{(i)} \subset \mc{F}}, and therefore the limit point \eqn{\ma^{\lpoint}} satisfies the constraint qualifications of the problem \eqref{con}.

@@

%\review{Let \eqn{\ma^{\lpoint}} be the limit point of the sequence of iterates \eqn{\{\iterate{\ma}{i}\}} generated by the algorithm \eqn{\mc{A}} as \eqn{i \to \infty}. The limit point \eqn{\ma^\lpoint} is a stationary point of \eqref{con} if it satisfies the \ac{KKT} conditions. 

@@

%%where \eqn{\mc{Y}^{\lpoint}} is the feasible set of \eqref{con-m} upon convergence, \textit{i.e.}, \eqn{\mc{Y}_{\lpoint}^{i}} as \eqn{i \to \infty}. 

@@

%Using (a),(b),(c) and (d), we can show that \eqn{\|\ma^{(i)} - \mc{A}(\ma^{(i)})\| \to 0} as \eqn{i \to \infty}, which is the limit point of the algorithm \eqn{\mc{A}}.

@@

%%In order for \eqn{\ma^{\lpoint}} to be stationary point, it must satisfy the \ac{KKT} conditions of \eqref{con}. In each iteration, the algorithm \eqn{\mc{A}} in \eqref{g-algo} finds a point \eqn{\iterate{\ma}{i} \in \mc{F}} with \eqn{f(\iterate{\ma}{i}) < f(\iterate{\ma}{i-1})}, therefore, it satisfies all the constraints of \eqref{con}. Since the feasible set is compact and strict monotonicity is ensured, as \eqn{i \to \infty}, the objective no longer decreases as the algorithm \eqn{\mc{A}(\ma^{\lpoint}) = \ma^{\lpoint}} finds a unique \eqn{\ma^{\lpoint} \in \mc{F}^{\lpoint}} due to the strong convexity of \eqn{f}.

@@

%%for some Lagrange multipliers \eqn{\mu_i \geq 0}. Using \eqref{con-relax} in \eqref{kkt_expr}, we can ensure the equivalence of the gradient between \eqref{con} and \eqref{con-m}. Moreover, \eqn{\ma^{\lpoint}} is a regular point \textit{i.e.} \eqn{\|\iterate{\ma}{i} - \iterate{\ma}{i+1} \| \to 0} as \eqn{i \to 0}. Now, with the above conditions and by using \cite[Th. 2 and 11]{scutari_1} and \cite[Prop. 3.2]{amir}, we can show that the fixed points obtained by \me{\mc{A}} under the mapping \me{f} is a stationary point of the nonconvex problem \eqref{con}.

@@

%To show the limit point of the sequence of iterates \me{\{\iterate{\ma}{i}\}} is a stationary point, it must satisfy the \ac{KKT} conditions of the problem in \eqref{con}. As \me{i \to \infty}, the objective converges as

@@

The following conditions are required to show the convergence of Algorithm \ref{algo-1}, which is used to solve problems \eqref{eqn-6} and \eqref{eqn-mse-1} in an iterative manner.
\begin{itemize}
\item[(a)] Objective function should be bounded below
\item[(b)] Feasible set should be compact
\item[(c)] Sequence of objective values should be strictly decreasing
\item[(d)] Uniqueness of the minimizer in each step.
\end{itemize}
\review{Note that condition (d) is required to ensure strict monotonicity of the objective sequence. Therefore, by using above conditions (a)-(c) along with \cite[Th. 3.14]{rudin1964principles}, we show the convergence objective sequence generated by Algorithm \ref{algo-1}. Then, by using the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1}, we show that \reviewF{every limit point of the sequence of iterates generated by Algorithm \ref{algo-1} is a stationary point of nonconvex problems \eqref{eqn-6} and \eqref{eqn-mse-1}}. The term iterates correspond to the stacked vector of solution variables obtained in each iteration.}

### 2015-10-28 Report/problem_formulation_intro.tex
updated stationarity

To minimize the total number of backlogged packets, we consider minimizing the weighted \me{\ell_{q}}-norm of the queue deviation objective as
\begin{equation} \label{eqn-4.2}
v_k =  Q_k - t_k = Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n})
\end{equation}
where \me{\gamma_{l,k,n}} is given by \eqref{eq:SINR} and the optimization variables are the transmit precoders \me{\mvec{m}{l,k,n}} and the receivers \me{\mvec{w}{l,k,n}}.

>>>>

In order to minimize the total number of backlogged packets, we consider minimizing the weighted \me{\ell_{q}}-norm of the queue deviation metric as
\begin{equation} \label{eqn-4.2}
v_k =  Q_k - t_k = Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n})
\end{equation}
where \me{\gamma_{l,k,n}} is given by \eqref{eq:SINR} and the optimization variables are transmit precoders \me{\mvec{m}{l,k,n}} and receive beamformers \me{\mvec{w}{l,k,n}}.
